---
output: 
    pdf_document:
        keep_tex: yes
        include:
          in_header: header.tex
urlcolor: blue
bibliography: mybibfile.bib
link-citations: yes
linkcolor: blue
csl: apa.csl
documentclass: revcoles
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi=1000,
                      dev="jpeg", out.width = '100%', out.height='100%', fig.pos="!h",
                      echo=FALSE)

library(carlians)
requeridos(knitr, ggplot2, tidyr, dplyr, kableExtra)
```
\begin{title}
\title[maintitle = Kurtosis effects on Estimating Structural Equation Models Over Different Sample Sizes,
       secondtitle = Efectos de la Kurtosis en la estimación de Modelos de Ecuaciones Estructurales bajo distintos tamaños de muestra,
       shorttitle = Short title in English
]
\end{title}

\begin{authors}
\author[firstname = César,
        surname = Gamboa-Sanabria,
        numberinstitution = 1,
        affiliation = Statistics Department University of Costa Rica, 
        email = info@cesargamboasanabria.com] \orcidicon{0000-0001-6733-4759}\,
\author[firstname = Andrés,
        surname = Arguedas-Leiva,
        numberinstitution = 1,
        affiliation = Statistics Department University of Costa Rica, 
        email = email]
\end{authors}

\begin{institutions}
     \institute[subdivision = {Statistics Department},
                division = Economic Sciences Faculty,
                institution = University of Costa Rica,
                city = San José,
                country = Costa Rica]
\end{institutions}

\begin{mainabstract}
 Insert your abstract here.
\keywords{SEM, simulation, kurtosis, lavaan}
\end{mainabstract}

\begin{secondaryabstract}
Inserte su resumen en aquí.
\keywords{SEM, simulación, kurtosis, lavaan}
\end{secondaryabstract}

\section{Introduction}  

```{r, child="01-Introduccion.Rmd"}
```

\section{Methodolgy} 

```{r, child="03-Metodologia.Rmd"}
```

\section{Results} 

```{r, child="04-Resultados.Rmd"}
```

\section{Conclusions}

```{r, child="05-Conclusiones.Rmd"}
```

\section{Appendices}

```{r, child="06-Anexos.Rmd"}
```

\section*{References}