---
title: |
    | UNIVERSIDAD DE COSTA RICA
    | SISTEMA DE ESTUDIOS DE POSGRADO
    | ESCUELA DE ESTADÍSTICA
    |
    |
    |
subtitle: |
    | TÍTULO IMPRESIONANTE
    |
    |
    |
    |
author: |
    |
    |
    |
    |
    |
    | CÉSAR ANDRÉS GAMBOA SANABRIA B12672
    | ANDRÉS ESTEBAN ARGUEDAS LEIVA B40535
    |
    |
    |
    |
    | Ciudad Universitaria Rodrigo Facio, Costa Rica
    |
    |
    |
date: "`r format(Sys.time(), '%Y')`"
always_allow_html: yes
header-includes:
   - \usepackage{amssymb}
output: 
    pdf_document:
        keep_tex: yes
        fig_caption: yes
        include:
          in_header: header.tex
urlcolor: blue
bibliography: mybibfile.bib
link-citations: yes
linkcolor: blue
csl: apa.csl
---

\pagenumbering{gobble}
\cleardoublepage

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi=1000,
                      dev="jpeg", out.width = '100%', out.height='100%', fig.pos="!h",
                      echo=FALSE)

library(carlians)
requeridos(knitr, ggplot2, tidyr, dplyr, kableExtra)

oldSource <- knit_hooks$get("source")
knit_hooks$set(source = function(x, options) {
  x <- oldSource(x, options)
  x <- ifelse(!is.null(options$ref), paste0("\\label{", options$ref,"}", x), x)
  ifelse(!is.null(options$codecap), paste0("\\captionof{chunk}{", options$codecap,"}", x), x)
})
```

\section*{RESUMEN}
\pagenumbering{gobble}

El Resumen

***Palabras clave***:kkk 
\cleardoublepage

\section*{ABSTRACT}
\pagenumbering{gobble}

El resumen en inglés

***Palabras clave***:kkk 
\cleardoublepage

\newpage


\pagenumbering{gobble}
\tableofcontents
\cleardoublepage
\pagenumbering{arabic}

\newpage

\section{INTRODUCCIÓN}  

```{r, child="01-Introduccion.Rmd"}
```


\newpage

\section{METODOLOGÍA} 

```{r, child="03-Metodologia.Rmd"}
```


\newpage

\section{RESULTADOS} 

```{r, child="04-Resultados.Rmd"}
```


\newpage

\section{CONCLUSIONES Y RECOMENDACIONES}

```{r, child="05-Conclusiones.Rmd"}
```

\newpage

\section{ANEXOS}

```{r, child="06-Anexos.Rmd"}
```

\section{REFERENCIAS}  

  